
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = NA)
```

# load packages
```{r}
packages <- c('terra','tidyverse','sf')
invisible(lapply(packages, library, character.only = TRUE))
library("rje") #expit, logit transformations
```

# set directories
```{r}
outDir<-"D:/Flood_Index/Data/Outputs/"
inDir<-"D:/Flood_Index/Data/Inputs/"
```

# Quality Filtering

Now we should do additional quality filtering.

In HLS, both value of 0 and 64 in the Fmask layer indicate the pixel without cloud, 
cloud shadow, water, or snow/ice. A value of 0 also shows climatology aerosol level 
and 64 shows low aerosol level. We will use these values to mask out poor quality 
pixels from the ndvi_stacks. HLS quality information can be found in section 6.5 
of the [HLS V2.0 User Guide](https://lpdaac.usgs.gov/documents/1118/HLS_User_Guide_V2.pdf).

```{r, warning=FALSE}
#nests_all_bands_clear<-nests_all_bands%>%
#  filter(!(FMask%in%c(0,64)))
nests_all_bands<-read.csv(paste0(outDir,"CT_nests_all_HLS_bands.csv"))

cloud_shadow_flag = function(pixel) {
  # reverse order of bits, left to right
  bit_str = paste(as.integer(intToBits(pixel)), collapse="")
  cloud = substr(bit_str, 1, 1) == '1' #based on pg 17 of HLS User Guide V2
  dilation = substr(bit_str, 2, 2) == '1'
  shadow = substr(bit_str, 3, 3) == '1'
  if(any(water,dilation,shadow)){return(1)}  else{return(0)}
}

clear_flag = function(pixel) {
  # reverse order of bits, left to right
  bit_str = paste(as.integer(intToBits(pixel)), collapse="")
  clear = substr(bit_str, 6, 6) == '1'|| substr(bit_str, 7, 7) == '1'#based on pg 17 of HLS User Guide V2
  if(clear){return(1)}  else{return(0)}
}
nests_all_bands_clear<-nests_all_bands%>%
  mutate(bit_str = paste(as.integer(intToBits(FMask)), collapse=""),
         cloud_shadow=ifelse(substr(bit_str, 1, 1) == '1'|substr(bit_str, 2, 2) == '1'|substr(bit_str, 3, 3) == '1',1,0),
         clear=ifelse(substr(bit_str, 6, 6) == '1'|substr(bit_str, 7, 7) == '1',1,0))
  

write.csv(nests_all_bands_clear,paste0(outDir,"CT_nests_all_HLS_bands_clear.csv"),row.names=F)
```