```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = NA)
```

# load packages
```{r}
packages <- c('terra','jsonlite','sp','httr',
              'rasterVis','tidyverse','magrittr','RColorBrewer','xml2','dygraphs',
              'xts','DT', 'rprojroot','sf','leaflet','imager')
invisible(lapply(packages, library, character.only = TRUE))
library("rje") #expit, logit transformations
```

# set directories
```{r}
outDir<-"D:/Flood_Index/Data/Outputs/"
inDir<-"D:/Flood_Index/Data/Inputs/"
```

# Set spatial regions of interest
```{r}
marsh<-terra::vect(paste0(inDir,"Nests/SALS_breeding_19Apr23.shp"))

marsh_sf<-st_as_sf(marsh)%>%
  sf::st_transform('+proj=longlat +datum=WGS84')


#slice into states to minimize the boundary extents
marsh_sf_list<-split(marsh_sf,marsh_sf$STATE)

#st_write(st_as_sf(st_as_sfc(st_bbox(marsh_sf_list[["CT"]]), crs=crs(marsh_sf_list[["CT"]]))),paste0(outDir,"CT_marsh_poly.geojson"))

```

# Load Queried RS image data
```{r}
load(file="Outputs/CT_NJ_NH_ME_bands_All_nest_data.Rdata")
```

#Load nest data
```{r}
#read in the time intervals for nest flood events
#thresh_nest_flood_events<-read.csv(paste0(outDir,"Nest_flood_events/nest_floods_26.7thresh.csv"))%>%
#  mutate(thresh_time_interval=interval(ymd_hms(str_extract(thresh_time_interval,".*--")),
#                                       ymd_hms(str_extract(thresh_time_interval,"--.*"))),
#         start_time=int_start(thresh_time_interval),
#         end_time=int_end(thresh_time_interval))
#convert to spatial points
#nests<-thresh_nest_flood_events%>%
#  filter(State!="NJ")%>% #we dont have images for NJ
#  distinct(lat, long, .keep_all=T)%>%
#  st_as_sf(coords=c("long","lat"),crs="EPSG:26918") #UTM18

nest_locations<-read.csv(paste0(inDir,"Nests/nest_locations_01_3_23.csv"))%>%
  rename(nest_id=id,site_name=Site,year=Year)%>%
  # Add nest identifying columns
  #add site names
  mutate(site=substr(nest_id,start=1,stop=2),
         #add nest number
         nest_num=as.numeric(substr(nest_id,(nchar(nest_id)-2),nchar(nest_id))))

fates<-read.csv(paste0(inDir,"Nests/NestFates_2001-2020.csv"),na.strings=c("","NOT REC","NA"))%>%
  #select and format variables
  dplyr::select("nest_id"="SHARPNestID","UltimateNestFate","FirstEggDate"="EstFirstEggDate",
                "maxeggs"="MaxNumEggs","Nsuccess"="NumFledged",
                "NumEggsFloodedInNest","NumEggsFloodedFromNest","NumEggsFloodedMissing",
                "NumChicksFlooded","NumChicksFloodedMissing",
                "NumEggsDepredated", "NumEggsDepredatedMissing","NumChicksDepredated","NumChicksDepredatedMissing")%>%
  mutate(across(c("NumEggsFloodedInNest","NumEggsFloodedFromNest","NumEggsFloodedMissing",
                  "NumChicksFlooded","NumChicksFloodedMissing","maxeggs","Nsuccess",
                  "NumEggsDepredated", "NumEggsDepredatedMissing","NumChicksDepredated","NumChicksDepredatedMissing"),
                as.numeric))%>%
  # Add nest identifying columns
  mutate(year=as.numeric(paste0("20",substr(nest_id,start=3,stop=4))),
         #add site names
         site=substr(nest_id,start=1,stop=2),
         #add nest number
         nest_num=as.numeric(substr(nest_id,(nchar(nest_id)-2),nchar(nest_id))))%>%
  # Format fate response variables
  rowwise()%>%
  # 1. proportion nestlings lost to flooding
  mutate(flooded_prop=sum(c(NumEggsFloodedInNest,NumEggsFloodedFromNest,NumEggsFloodedMissing,
                            NumChicksFlooded,NumChicksFloodedMissing),na.rm = T),
         flooded_prop=round(flooded_prop/maxeggs,2),
         # 2. Probability nest failed/was successful in general
         fate=case_when(
           UltimateNestFate%in%c("FLEDGED")~1,
           UltimateNestFate%in%c("DEPREDATED","FLOODED","FLOODED/DEPREDATED","NEVER HAD EGGS","NEVER HAD","FAIL UNKNOWN")~0,
           !(UltimateNestFate%in%c("FLEDGED","DEPREDATED","FLOODED","FLOODED/DEPREDATED",
                                   "NEVER HAD EGGS","NEVER HAD","FAIL UNKNOWN"))~NA),
         # 3. Probability nest failed due to flooding
         flooded_fate=ifelse(UltimateNestFate%in%c("FLOODED","FLOODED/DEPREDATED"),1,0))%>%
  ungroup()%>%
  select(nest_id,FirstEggDate, year, site, nest_num, flooded_prop,fate,flooded_fate)

#set all fate variables to NA for nests with NA for ultimate nest fate
fates[is.na(fates$fate),c(6,8)]<-NA
fates[is.nan(fates$flooded_prop),6]<-NA

nests<-left_join(nest_locations,fates,by=c("nest_id","year","site","nest_num"))%>%
  distinct(nest_id,.keep_all = T)%>%
  mutate(FirstEggDate=mdy(FirstEggDate))%>%
  #convert to spatial points
  st_as_sf(coords=c("long","lat"),crs="EPSG:26918")#UTM18
```

# Access and Interact with the HLS data you queried

```{r, results= "hide"}
#Set up rgdal configurations to access the cloud assets that we are interested in.
#You can learn more about these configuration options [here](https://trac.osgeo.org/gdal/wiki/ConfigOptions). 
setGDALconfig("GDAL_HTTP_UNSAFESSL", value = "YES")
setGDALconfig("GDAL_HTTP_COOKIEFILE", value = ".rcookies")
setGDALconfig("GDAL_HTTP_COOKIEJAR", value = ".rcookies")
setGDALconfig("GDAL_DISABLE_READDIR_ON_OPEN", value = "EMPTY_DIR")
setGDALconfig("CPL_VSIL_CURL_ALLOWED_EXTENSIONS", value = "TIF")
```



## Subset HLS COGs Spatially and Stack HLS Data Layers
Below, convert the state regions of interest projections into the native projection 
of HLS, UTM (aligned to the Military Grid Reference System). This must be done 
in order to use the Regions of Interest (ROIs) to subset the image files.
If you have trouble running the code chunk below, make sure your credentials are 
entered correctly in the created netrc file.

```{r, warning=FALSE}
# Extract the CRS from one of the assets for each state region
coord_ref_ct <- terra::rast(paste0(state_list[["CT"]]$Asset_Link[1])) 
coord_ref_nj <- terra::rast(paste0(state_list[["NJ"]]$Asset_Link[1]))
coord_ref_nh <- terra::rast(paste0(state_list[["NH"]]$Asset_Link[1]))  
coord_ref_me <- terra::rast(paste0(state_list[["ME"]]$Asset_Link[1]))  

# set each state to its UTM coordinate system (that's what the HLS data is in)
marsh_sf_list[["CT18"]]<-st_transform(marsh_sf_list[["CT"]],crs(coord_ref_ct))
marsh_sf_list[["CT19"]]<-st_transform(marsh_sf_list[["CT"]],crs(coord_ref_nh))
marsh_sf_list[["NJ"]]<-st_transform(marsh_sf_list[["NJ"]],crs(coord_ref_nj))
marsh_sf_list[["NH"]]<-st_transform(marsh_sf_list[["NH"]],crs(coord_ref_nh))
marsh_sf_list[["ME"]]<-st_transform(marsh_sf_list[["ME"]],crs(coord_ref_me))
```

Below, we create a list of raster layers for each of our bands of interest 
(e.g., Red, NIR, Fmask...). Next each band is read into the memory and then 
cropped to our area of interest. The Cropped raster will be stacked and  We'll use 
these stacks to calculate water classifications and mask 
for cloud contamination. 

Note that the `raster` function is making a separate 
request for each data layer located in the Cumulus cloud archive. This takes time,
and the more data layers we have in the time series, the longer this cell takes to
run.  

```{r, warning=FALSE, results= "hide"}

blue_stack<-green_stack<-red_stack<-nir_stack<-swir1_stack<-swir2_stack<-therm1_stack<-therm2_stack<-fmask_stack<- date_list<-list()

l <- m <- n <-o <- p<- q<- r<- s<- u<- 0

# Do this by state region
for (state in names(state_list)){
  search_df_state<- state_list[[state]]
  if(state!="CT"){
  roi<-marsh_sf_list[[state]]
  }
# for each band image across all scenes of all state events
for (row in seq(length(search_df_state$band))){
    #is it a thermal 2 image?
  if (search_df_state$band[row]=="B11" && substr(search_df_state$Collection[row],4,4)=="L"){
    l = l+1
        #read in band image
    therm2 <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
    if(state!="CT"){
        #crop to ROI
    therm2_crop <- terra::mask(terra::crop(therm2, terra::ext(roi)), roi)
    therm2_stack[[l]] <- therm2_crop
    }else if(state=="CT" && crs(therm2)==crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    therm2_crop <- terra::mask(terra::crop(therm2, terra::ext(marsh_sf_list[["CT18"]])), marsh_sf_list[["CT18"]])
    therm2_stack[[l]] <- therm2_crop
    }else if(state=="CT" && crs(therm2)!=crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    therm2_crop <- terra::mask(terra::crop(therm2, terra::ext(marsh_sf_list[["CT19"]])), marsh_sf_list[["CT19"]])
    therm2_stack[[l]] <- therm2_crop
    }
    rm(therm2, therm2_crop)
    
    #is it a thermal 1 image?
  }else if(search_df_state$band[row]=="B10" && substr(search_df_state$Collection[row],4,4)=="L"){
    m = m+1
        #read in band image
    therm1 <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
    if(state!="CT"){
        #crop to ROI
    therm1_crop <- terra::mask(terra::crop(therm1, terra::ext(roi)), roi)
    therm1_stack[[m]] <- therm1_crop
    }else if(state=="CT" && crs(therm1)==crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    therm1_crop <- terra::mask(terra::crop(therm1, terra::ext(marsh_sf_list[["CT18"]])), marsh_sf_list[["CT18"]])
    therm1_stack[[m]] <- therm1_crop
    }else if(state=="CT" && crs(therm1)!=crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    therm1_crop <- terra::mask(terra::crop(therm1, terra::ext(marsh_sf_list[["CT19"]])), marsh_sf_list[["CT19"]])
    therm1_stack[[m]] <- therm1_crop
    }
    rm (therm1, therm1_crop)
    
    #is it a swir 2 image?
  }else if (search_df_state$band[row] %in% c('B07','B12')){
    n = n+1
        #read in band image
    swir2 <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
    if(state!="CT"){
        #crop to ROI
    swir2_crop <- terra::mask(terra::crop(swir2, terra::ext(roi)), roi)
    swir2_stack[[n]] <- swir2_crop
    }else if(state=="CT"&crs(swir2)==crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    swir2_crop <- terra::mask(terra::crop(swir2, terra::ext(marsh_sf_list[["CT18"]])), marsh_sf_list[["CT18"]])
    swir2_stack[[n]] <- swir2_crop
    }else if(state=="CT"&crs(swir2)!=crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    swir2_crop <- terra::mask(terra::crop(swir2, terra::ext(marsh_sf_list[["CT19"]])), marsh_sf_list[["CT19"]])
    swir2_stack[[n]] <- swir2_crop
    }
    rm (swir2, swir2_crop)
    
    #is it a swir 1 image?
  }else if (search_df_state$band[row]=='B06' || (search_df_state$band[row]=='B11'&& substr(search_df_state$Collection[row],4,4)=="S")){
    o = o+1
        #read in band image
    swir1 <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
    if(state!="CT"){
        #crop to ROI
    swir1_crop <- terra::mask(terra::crop(swir1, terra::ext(roi)), roi)
    swir1_stack[[o]] <- swir1_crop
    }else if(state=="CT"&crs(swir1)==crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    swir1_crop <- terra::mask(terra::crop(swir1, terra::ext(marsh_sf_list[["CT18"]])), marsh_sf_list[["CT18"]])
    swir1_stack[[o]] <- swir1_crop
    }else if(state=="CT"&crs(swir1)!=crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    swir1_crop <- terra::mask(terra::crop(swir1, terra::ext(marsh_sf_list[["CT19"]])), marsh_sf_list[["CT19"]])
    swir1_stack[[o]] <- swir1_crop
    }
    rm (swir1, swir1_crop)
    
    #is it a NIR image?
  }else if (search_df_state$band[row] %in% c('B05','B8A')){
    p = p+1
    nir <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
    if(state!="CT"){
    nir_crop <- terra::mask (terra::crop(nir, terra::ext(roi)), roi)
    nir_stack[[p]] <- nir_crop
    }else if(state=="CT"&crs(nir)==crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    nir_crop <- terra::mask(terra::crop(nir, terra::ext(marsh_sf_list[["CT18"]])), marsh_sf_list[["CT18"]])
    nir_stack[[p]] <- nir_crop
    }else if(state=="CT"&crs(nir)!=crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    nir_crop <- terra::mask(terra::crop(nir, terra::ext(marsh_sf_list[["CT19"]])), marsh_sf_list[["CT19"]])
    nir_stack[[p]] <- nir_crop
    }  
    rm(nir, nir_crop)
    
    # is it a red image?
  }else if (search_df_state$band[row]=='B04'){
    q = q+1
        #read in band image
    red <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
    if(state!="CT"){
        #crop to ROI
    red_crop <- terra::mask(terra::crop(red, terra::ext(roi)), roi)
    red_stack[[q]] <- red_crop
    }else if(state=="CT"&crs(red)==crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    red_crop <- terra::mask(terra::crop(red, terra::ext(marsh_sf_list[["CT18"]])), marsh_sf_list[["CT18"]])
    red_stack[[q]] <- red_crop
    }else if(state=="CT"&crs(red)!=crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    red_crop <- terra::mask(terra::crop(red, terra::ext(marsh_sf_list[["CT19"]])), marsh_sf_list[["CT19"]])
    red_stack[[q]] <- red_crop
    }
    rm (red, red_crop)
    
    #is it a blue image?
  }else if (search_df_state$band[row]=='B02'){
    r = r+1
        #read in band image
    blue <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
    if(state!="CT"){
        #crop to ROI
    blue_crop <- terra::mask(terra::crop(blue, terra::ext(roi)), roi)
    blue_stack[[r]] <- blue_crop
    }else if(state=="CT"&crs(blue)==crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    blue_crop <- terra::mask(terra::crop(blue, terra::ext(marsh_sf_list[["CT18"]])), marsh_sf_list[["CT18"]])
    blue_stack[[r]] <- blue_crop
    }else if(state=="CT"&crs(blue)!=crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    blue_crop <- terra::mask(terra::crop(blue, terra::ext(marsh_sf_list[["CT19"]])), marsh_sf_list[["CT19"]])
    blue_stack[[r]] <- blue_crop
    }
    rm (blue, blue_crop)
    
    #is it a green image?
  }else if (search_df_state$band[row]=='B03'){
    s = s+1
        #read in band image
    green <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
    if(state!="CT"){
        #crop to ROI
    green_crop <- terra::mask(terra::crop(green, terra::ext(roi)), roi)
    green_stack[[s]] <- green_crop
    }else if(state=="CT"&crs(green)==crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    green_crop <- terra::mask(terra::crop(green, terra::ext(marsh_sf_list[["CT18"]])), marsh_sf_list[["CT18"]])
    green_stack[[s]] <- green_crop
    }else if(state=="CT"&crs(green)!=crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    green_crop <- terra::mask(terra::crop(green, terra::ext(marsh_sf_list[["CT19"]])), marsh_sf_list[["CT19"]])
    green_stack[[s]] <- green_crop
    }
    rm (green, green_crop)
    
    #is it a Quality image?
  }else if (search_df_state$band[row]=='Fmask'){
    u = u+1
        #read in band image
    fmask <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
    if(state!="CT"){
        #crop to ROI
    fmask_crop <- terra::mask(terra::crop(fmask, terra::ext(roi)), roi)
    fmask_stack[[u]] <- fmask_crop
    }else if(state=="CT"&crs(fmask)==crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    fmask_crop <- terra::mask(terra::crop(fmask, terra::ext(marsh_sf_list[["CT18"]])), marsh_sf_list[["CT18"]])
    fmask_stack[[u]] <- fmask_crop
    
    }else if(state=="CT"&crs(fmask)!=crs(marsh_sf_list[["CT18"]])){
          #crop to ROI
    fmask_crop <- terra::mask(terra::crop(fmask, terra::ext(marsh_sf_list[["CT19"]])), marsh_sf_list[["CT19"]])
    fmask_stack[[u]] <- fmask_crop
    }
    
    # also record the image information and add to a matching index list
    doy_time = strsplit(sources(fmask), "[.]")[[1]][14]
    doy = substr(doy_time, 1, 7)
    date <- as.Date(as.integer(substr(doy,5,7)), origin = paste0(substr(doy,1,4), "-01-01"))
    time <- paste(substr(doy_time, 9, 10),substr(doy_time, 11, 12),sep=":")
    
    if (strsplit(sources(fmask), "[.]")[[1]][12] == 'S30'){
      date_list[[u]] <- paste0('S',as.character(date),'T',time)
    }else{
      date_list[[u]] <- paste0('L',as.character(date),'T',time)
    }
    rm (fmask, fmask_crop)
    
  }
}
}


save(list=c("blue_stack","green_stack","red_stack","nir_stack","swir1_stack","swir2_stack","therm1_stack","therm2_stack"), file="Outputs/band_stacks_all_nests_NJ_CT_NH_ME.Rdata")
```

# Calculate water indices

Now we can start asking our science questions. First we define the water classification functions 
and then execute them on the band data loaded into memory. After that, we can perform 
quality filtering to screen out any poor-quality observations.

Create a function to calculate FLATS, TC Wetness, and NDWI/Pheno indices to create FLATS coefficients calibrated to our data.

```{r}
calculate_flats <- function(red, swir1, green){
ndwi <- (red-swir1)/(red+swir1)
pheno <- (green-red)/(green+red)
flats<- expit(-1.6+20*ndwi+68.6*pheno) #expit back transforms into response values from GLM logit transformation
return(flats)
}

calculate_ndwi <- function(red, swir1){
ndwi <- (red-swir1)/(red+swir1)
return(ndwi)
}

calculate_pheno <- function(green,red){
pheno <- (green-red)/(green+red)
return(pheno)
}

calculate_tcwet <- function(blue,green,red,nir,swir1,swir2){
tcwet<-(0.1509*blue)+(0.1973*green)+(0.3279*red)+(0.3406*nir)-(0.7112*swir1)-(0.4572*swir2)
return(tcwet)
}

# test set of thresholds to see which cut off leads to the most accurate predictions
```

Now we can calculate variables needed to create water indices from the stacked band rasters. We will
create layer names from the dates the data is captured, along with the
first letter of **L** and **S** shows which sensor is data from.

```{r, warning=FALSE}
flats_stack<-list()
for (i in 1:length(red_stack)){ 
  # Calculate FLATS 
  flats_stack[[i]] <- calculate_flats(red_stack[[i]],swir1_stack[[i]], green_stack[[i]])  
  # Exclude the Inf and -Inf values
  flats_stack[[i]][flats_stack[[i]] == Inf] <- NA
  flats_stack[[i]][flats_stack[[i]] == -Inf] <- NA
}
names(flats_stack) <- unlist(date_list)


ndwi_stack <- list()
for (i in 1:length(red_stack)){ 
  # Calculate NDWI 
  ndwi_stack[[i]] <- calculate_ndwi(red_stack[[i]],swir1_stack[[i]])  
  # Exclude the Inf and -Inf values
  ndwi_stack[[i]][ndwi_stack[[i]] == Inf] <- NA
  ndwi_stack[[i]][ndwi_stack[[i]] == -Inf] <- NA
  
}
names(ndwi_stack) <- unlist(date_list)



pheno_stack <- list()
for (i in 1:length(red_stack)){ 
  # Calculate PHENO 
  pheno_stack[[i]] <- calculate_pheno(green_stack[[i]],red_stack[[i]])  
  # Exclude the Inf and -Inf values
  pheno_stack[[i]][pheno_stack[[i]] == Inf] <- NA
  pheno_stack[[i]][pheno_stack[[i]] == -Inf] <- NA
}
names(pheno_stack) <- unlist(date_list)




tcwet_stack <- list()
for (i in 1:length(red_stack)){ 
  # Calculate TCWET 
  tcwet_stack[[i]] <- calculate_tcwet(blue_stack[[i]],green_stack[[i]],red_stack[[i]],nir_stack[[i]],swir1_stack[[i]],swir2_stack[[i]])  
  # Exclude the Inf and -Inf values
  tcwet_stack[[i]][tcwet_stack[[i]] == Inf] <- NA
  tcwet_stack[[i]][tcwet_stack[[i]] == -Inf] <- NA
}
names(tcwet_stack) <- unlist(date_list)



#also name the QA bands with date-state 
names(fmask_stack) <- unlist(date_list)
```


Now extract pixel values that contain nest locations
```{r}
flats_pix<-ndwi_pix<-pheno_pix<-tcwet_pix<- fmask_pix<-list()

for (i in 1:nrow(nests)){
  # extract pixel FLATS values at each location
flats_pix[[i]]<-lapply(flats_stack,function(x) terra::extract(x,terra::project(vect(nests[i,]), crs(x))))
flats_pix[[i]]<-do.call('rbind',lapply(flats_pix[[i]],function(x){
  names(x)<-c("ID","flats")
  return(x)
}))
flats_pix[[i]]<-flats_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = flats)

# extract pixel NDWI values at each location
ndwi_pix[[i]]<-lapply(ndwi_stack,function(x) terra::extract(x,terra::project(vect(nests[i,]), crs(x))))
ndwi_pix[[i]]<-do.call('rbind',lapply(ndwi_pix[[i]],function(x){
  names(x)<-c("ID","ndwi")
  return(x)
}))
ndwi_pix[[i]]<-ndwi_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = ndwi)

# extract pixel PHENO values at each location
pheno_pix[[i]]<-lapply(pheno_stack,function(x) terra::extract(x,terra::project(vect(nests[i,]), crs(x))))
pheno_pix[[i]]<-do.call('rbind',lapply(pheno_pix[[i]],function(x){
  names(x)<-c("ID","pheno")
  return(x)
}))
pheno_pix[[i]]<-pheno_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = pheno)

# extract pixel TCWET values at each location
tcwet_pix[[i]]<-lapply(tcwet_stack,function(x) terra::extract(x,terra::project(vect(nests[i,]), crs(x))))
tcwet_pix[[i]]<-do.call('rbind',lapply(tcwet_pix[[i]],function(x){
  names(x)<-c("ID","tcwet")
  return(x)
}))
tcwet_pix[[i]]<-tcwet_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = tcwet)

#extract pixel QA values at each location
fmask_pix[[i]]<-lapply(fmask_stack,function(x) terra::extract(x,terra::project(vect(nests[i,]), crs(x))))
fmask_pix[[i]]<-do.call('rbind',lapply(fmask_pix[[i]],function(x){
  names(x)<-c("ID","fmask")
  return(x)
}))
fmask_pix[[i]]<-fmask_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = fmask)

}
  #combines all the band extraction columns into one table like cbind
flats_pix2<-do.call('rbind',flats_pix)%>%
  arrange(ID)%>%
  cbind(nests[,1:3])%>%
  dplyr::select(-ID)

ndwi_pix2<-do.call('rbind',ndwi_pix)%>%
  arrange(ID)%>%
  cbind(nests[,1:3])%>%
  dplyr::select(-ID)

pheno_pix2<-do.call('rbind',pheno_pix)%>%
  arrange(ID)%>%
  cbind(nests[,1:3])%>%
  dplyr::select(-ID)

tcwet_pix2<-do.call('rbind',tcwet_pix)%>%
  arrange(ID)%>%
  cbind(nests[,1:3])%>%
  dplyr::select(-ID)

fmask_pix2<-do.call('rbind',fmask_pix)%>%
  arrange(ID)%>%
  cbind(nests[,1:3])%>%
  dplyr::select(-ID)

```

# Transform each metric into a binary flood indicator
```{r}
# Function to extract whether a pixel is water from bit coded QA values 
water_flag = function(fmask) {
  # reverse order of bits, left to right
  bit_str = paste(as.integer(intToBits(fmask)), collapse="")
  water = substr(bit_str, 6, 6) == '1' #bit 6 if you start counting from bit 0 as place 1.
  if(water){return(1)}  else{return(0)}
}


```

Now we plot! Let's star with the first item in NDVI time series.

```{r, warning=FALSE, message=FALSE}
# Create a color palette 
pal <- colorNumeric(terrain.colors(n = 100), c(0,1) ,na.color = "transparent", reverse = TRUE)

leaflet() %>% 
    addProviderTiles(providers$Esri.WorldImagery) %>%
    addRasterImage(ndvi_stacks[[1]], color = pal, opacity = 1) %>%
    addPolygons(data = cropland_geojson, fill = FALSE) %>%
    addMiniMap(zoomLevelFixed = 5) %>%
    leaflet::addLegend(pal = pal, values = c(0,1), title = "NDVI")

```

------------------------------------------------------------------------

## 4b. Quality Filtering

Now we should do additional quality filtering.

In HLS, both value of 0 and 64 in the Fmask layer indicate the pixel without cloud, 
cloud shadow, water, or snow/ice. A value of 0 also shows climatology aerosol level 
and 64 shows low aerosol level. We will use these values to mask out poor quality 
pixels from the ndvi_stacks. HLS quality information can be found in section 6.5 
of the [HLS V2.0 User Guide](https://lpdaac.usgs.gov/documents/1118/HLS_User_Guide_V2.pdf).

Create a stack of masked rasters and mask poor quality pixels.



```{r, warning=FALSE}
mask_raster <- list()
ndvi_filtered <- list()

for (i in 1:length(fmask_stack)){
  mask_raster[[i]] <- fmask_stack[[i]]
  mask_raster[[i]][values(mask_raster[[i]])!= 0 || values(mask_raster[[i]])!= 64] <- NA
  ndvi_filtered[[i]] <- mask(ndvi_stacks[[i]], mask_raster[[i]], maskvalue=NA )
  names(ndvi_filtered[[i]]) <- names(ndvi_stacks[[i]])
}
ndvi_filtered_stacks <- terra::rast(ndvi_filtered)
```

------------------------------------------------------------------------

## 4c.Visualize Quality Filtered Stacked Time Series

Now we can plot multiple layers to create an interactive NDVI time
series map with `leaflet`. Click on the dates on the left side to view
the layer.

```{r, warning=FALSE, message=FALSE}

base<-c('map<-leaflet()%>%
            addProviderTiles(providers$Esri.WorldImagery) %>%
            addMiniMap(zoomLevelFixed = 5) %>%')

# make a string including the addRasterImage function for every layer in the raster stack
X <- lapply(1:nlyr(ndvi_filtered_stacks), function(j){
    paste(paste("addRasterImage(ndvi_filtered_stacks[[",j,"]],
             colors = pal,
             opacity=1,
             group=names(ndvi_filtered_stacks[[",j,"]]))", sep=""),"%>% \n")})

X <- do.call(paste, X)

controls<-"addLayersControl(baseGroups=names(ndvi_stacks),
               options = layersControlOptions(collapsed=F), position = 'topleft')%>%"

legend <- "leaflet::addLegend(pal = pal, values = c(0,1), title = 'NDVI')"

final <- paste(base, X, controls, legend ,sep="\n")
eval(parse(text=final))
map
```

Above, the time series show the changes in NDVI over the two months of September 
and August 2021. The NDVI values over these agricultural fields are high and stable 
and then they drastically decrease showing that they are cultivated before the send of September. 



------------------------------------------------------------------------

## 4d. Export Statistics

Below, plot the time series as boxplots showing the distribution of NDVI values 
for our farm fields.

```{r, fig.width=15}
raster::boxplot(ndvi_filtered_stacks, col=c('olivedrab3'),  main='NDVI Time Series', ylab='NDVI', names = names(ndvi_stacks), las=2)
```

Next, calculate the statistics for each observation and export to CSV. Quality 
filtered raster stack is used to calculate the statistics.

```{r}
ndvi_mean <- terra::global(ndvi_filtered_stacks, 'mean', na.rm=TRUE)
ndvi_max <- terra::global(ndvi_filtered_stacks, 'max', na.rm=TRUE)
ndvi_min <- terra::global(ndvi_filtered_stacks, 'min', na.rm=TRUE)
ndvi_sd <- terra::global(ndvi_filtered_stacks, 'sd', na.rm=TRUE)
#ndvi_median <- terra::global(ndvi_filtered_stacks, 'median', na.rm=TRUE)    # the global function does not have median
```

Make interactive plots of raster statistics using `dygraphs` library. The date is 
formatted using `lubridate` package and `xts` package is used to transform the 
dataframe to the xts format.

```{r}
stats <- data.frame(
  Date=substr(names(ndvi_filtered_stacks), 2,11),
  NDVI_Max = ndvi_max,
  NDVI_Min = ndvi_min,
  #NDVI_Median = ndvi_median,
  NDVI_mean = ndvi_mean,
  NDVI_SD = ndvi_sd
)
stats$Date <- ymd(stats$Date)                      # reformat the date
variables = xts(x=stats[,-1], order.by=stats$Date) # Choose the cols with the variables
dygraph(variables)
```

If you want to export these statistics, we can do so to a CSV file.

```{r}
stats_name <- file.path(outDir, "NDVI_Statistics.csv")
write.csv(stats,stats_name)
```

------------------------------------------------------------------------

# 5. Export Output to GeoTIFF

Finally, if you want to capture the final output files locally on your
machine, you can export the output files as GeoTIFFs.

```{r, warning = FALSE}
for (i in 1:length(ndvi_filtered)){
  output_name <- file.path(outDir, paste0(names(ndvi_filtered[[i]]), "_NDVI.tif"))
  terra::writeRaster(ndvi_filtered[[i]], output_name, overwrite = TRUE)
}
```

The raster stack object can also be written to the disk.

```{r, warning=FALSE}
output_name <- file.path(outDir, "NDVI_stack.tif")
terra::writeRaster(ndvi_filtered_stacks ,filename=output_name, overwrite=TRUE)
```


And we're done! You have successfully analyzed
data in the cloud, exporting just the information you needed for your area 
of interest rather than having to download everything.


Now, the cropped and stacked rasters are loaded into memory without being 
downloaded. Running the code below should confirm this is true.

```{r}
inMemory(nir_stack[[1]])

t<-do.call("rbind",state_list)
count(t,band)
```