```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(comment = NA)
```

# load packages
```{r}
packages <- c('terra','jsonlite','sp',
              'rasterVis','tidyverse','magrittr','RColorBrewer','xml2','dygraphs',
              'xts','DT', 'rprojroot','sf','imager','tidyterra')
invisible(lapply(packages, library, character.only = TRUE))

```

# set directories
```{r}
outDir<-"D:/Flood_Index/Data/Outputs/"
inDir<-"D:/Flood_Index/Data/Inputs/"
```

#set the path to your netrc file. This has your login credentials for NASA earthdata.
```{r}
source("Functions/earthdata_netrc_setup.R")
```

# Set spatial regions of interest
```{r}
marsh<-terra::vect(paste0(inDir,"Nests/SALS_breeding_19Apr23.shp"))

marsh_sf<-st_as_sf(marsh)%>%
  sf::st_transform('+proj=longlat +datum=WGS84')


#slice into states to minimize the boundary extents
marsh_sf_list<-split(marsh_sf,marsh_sf$STATE)

#st_write(st_as_sf(st_as_sfc(st_bbox(marsh_sf_list[["CT"]]), crs=crs(marsh_sf_list[["CT"]]))),paste0(outDir,"CT_marsh_poly.geojson"))

```

# Load Queried RS image data
```{r}
load(file="Outputs/CT_NJ_NH_ME_bands_All_nest_data.Rdata") #CT, NJ, NH, ME 2013-2020, May 15-Aug01
```

#Load nest data
```{r}
nest_shp<-st_read(paste0(inDir,"Nests/nest_locations_01_3_23.shp"))%>%
  rename(nest_id=id,site=site_cd,year=Year)%>%
  select(nest_id,site,year)
nest_locations<-read.csv(paste0(inDir,"Nests/nest_locations_01_3_23.csv"))%>%
  rename(nest_id=id,site=Site,year=Year)%>%
  # Add nest identifying columns
  #add site names
  mutate(site=substr(nest_id,start=1,stop=2),
         #add nest number
         nest_num=as.numeric(substr(nest_id,(nchar(nest_id)-2),nchar(nest_id))))

fates<-read.csv(paste0(inDir,"Nests/NestFates_2001-2020.csv"),na.strings=c("","NOT REC","NA"))%>%
  #select and format variables
  dplyr::select("nest_id"="SHARPNestID","UltimateNestFate","FirstEggDate"="EstFirstEggDate",
                "maxeggs"="MaxNumEggs","Nsuccess"="NumFledged",
                "NumEggsFloodedInNest","NumEggsFloodedFromNest","NumEggsFloodedMissing",
                "NumChicksFlooded","NumChicksFloodedMissing",
                "NumEggsDepredated", "NumEggsDepredatedMissing","NumChicksDepredated","NumChicksDepredatedMissing")%>%
  mutate(across(c("NumEggsFloodedInNest","NumEggsFloodedFromNest","NumEggsFloodedMissing",
                  "NumChicksFlooded","NumChicksFloodedMissing","maxeggs","Nsuccess",
                  "NumEggsDepredated", "NumEggsDepredatedMissing","NumChicksDepredated","NumChicksDepredatedMissing"),
                as.numeric))%>%
  # Add nest identifying columns
  mutate(year=as.numeric(paste0("20",substr(nest_id,start=3,stop=4))),
         #add site names
         site=substr(nest_id,start=1,stop=2),
         #add nest number
         nest_num=as.numeric(substr(nest_id,(nchar(nest_id)-2),nchar(nest_id))))%>%
  # Format fate response variables
  rowwise()%>%
  # 1. proportion nestlings lost to flooding
  mutate(flooded_prop=sum(c(NumEggsFloodedInNest,NumEggsFloodedFromNest,NumEggsFloodedMissing,
                            NumChicksFlooded,NumChicksFloodedMissing),na.rm = T),
         flooded_prop=round(flooded_prop/maxeggs,2),
         # 2. Probability nest failed/was successful in general
         fate=case_when(
           UltimateNestFate%in%c("FLEDGED")~1,
           UltimateNestFate%in%c("DEPREDATED","FLOODED","FLOODED/DEPREDATED","NEVER HAD EGGS","NEVER HAD","FAIL UNKNOWN")~0,
           !(UltimateNestFate%in%c("FLEDGED","DEPREDATED","FLOODED","FLOODED/DEPREDATED",
                                   "NEVER HAD EGGS","NEVER HAD","FAIL UNKNOWN"))~NA),
         # 3. Probability nest failed due to flooding
         flooded_fate=ifelse(UltimateNestFate%in%c("FLOODED","FLOODED/DEPREDATED"),1,0))%>%
  ungroup()%>%
  select(nest_id,FirstEggDate, year, site, nest_num, flooded_prop,fate,flooded_fate)

#set all fate variables to NA for nests with NA for ultimate nest fate
fates[is.na(fates$fate),c(6,8)]<-NA
fates[is.nan(fates$flooded_prop),6]<-NA

nests<-left_join(nest_locations,fates,by=c("nest_id","year","site","nest_num"))%>%
  distinct(nest_id,.keep_all = T)%>%
  mutate(FirstEggDate=mdy(FirstEggDate))
nests<-left_join(nest_shp,nests,by = c("nest_id","year","site"))
```

# Access and Interact with the HLS data you queried

```{r, results= "hide"}
#Set up rgdal configurations to access the cloud assets that we are interested in.
#You can learn more about these configuration options [here](https://trac.osgeo.org/gdal/wiki/ConfigOptions). 
setGDALconfig("GDAL_HTTP_UNSAFESSL", value = "YES")
setGDALconfig("GDAL_HTTP_COOKIEFILE", value = ".rcookies")
setGDALconfig("GDAL_HTTP_COOKIEJAR", value = ".rcookies")
setGDALconfig("GDAL_DISABLE_READDIR_ON_OPEN", value = "EMPTY_DIR")
setGDALconfig("CPL_VSIL_CURL_ALLOWED_EXTENSIONS", value = "TIF")
```



## Subset HLS COGs Spatially and Stack HLS Data Layers
Below, convert the state regions of interest projections into the native projection 
of HLS, UTM (aligned to the Military Grid Reference System). This must be done 
in order to use the Regions of Interest (ROIs) to subset the image files.
If you have trouble running the code chunk below, make sure your credentials are 
entered correctly in the created netrc file.

```{r, warning=FALSE}
# Extract the CRS from one of the assets for each state region
coord_ref_ct <- terra::rast(paste0(state_list[["CT"]]$Asset_Link[1])) 
coord_ref_nj <- terra::rast(paste0(state_list[["NJ"]]$Asset_Link[1]))
coord_ref_nh <- terra::rast(paste0(state_list[["NH"]]$Asset_Link[1]))  
coord_ref_me <- terra::rast(paste0(state_list[["ME"]]$Asset_Link[1]))  

# set each state to its UTM coordinate system (that's what the HLS data is in)
marsh_sf_list[["CT"]]<-st_transform(marsh_sf_list[["CT"]],terra::crs(coord_ref_ct))#make sure this is UTM 18
marsh_sf_list[["NJ"]]<-st_transform(marsh_sf_list[["NJ"]],terra::crs(coord_ref_nj))
marsh_sf_list[["NH"]]<-st_transform(marsh_sf_list[["NH"]],terra::crs(coord_ref_nh))
marsh_sf_list[["ME"]]<-st_transform(marsh_sf_list[["ME"]],terra::crs(coord_ref_me))
```

Below, we create a list of raster layers for each of our bands of interest 
(e.g., Red, NIR, Fmask...). Next each band is read into the memory and then 
cropped to our area of interest. The Cropped raster will be stacked and  We'll use 
these stacks to calculate water classifications and mask 
for cloud contamination. 

Note that the `raster` function is making a separate 
request for each data layer located in the Cumulus cloud archive. This takes time,
and the more data layers we have in the time series, the longer this cell takes to
run.  


```{r, warning=FALSE, results= "hide"}
#writeRaster(fmask_stack[[1]],paste0(outDir,"CTmarsh_UTM18_30mraster_template.tif"))
# template raster to align CT images in UTM 19 to a standard CRS and extent
ct18_temp<-terra::rast(paste0(outDir,"CTmarsh_UTM18_30mraster_template.tif"))


# Do this by state region
    # specify state -names(state_list)
state="CT"

    # places to hold the cropped bands across all images
blue_stack<-green_stack<-red_stack<-nir_stack<-swir1_stack<-swir2_stack<-therm1_stack<-therm2_stack<-fmask_stack<- date_list<-list()

    # markers for each band list (should correspond with image index number)
l <- m <- n <-o <- p<- q<- r<- s<- u<- 0

    # pull the image query results that correspond with the state
  search_df_state<- state_list[[state]]

    # if the state is connecticut, don't use a standard ROI, we need to specify whether its UTM18 or 19, image by image.
  if(state!="CT"){
  roi<-marsh_sf_list[[state]]
  }
  
    #subset nest data to state region
  nests_state<-nests%>%
  filter(State==state,year>=2013,Species=="SALS")
  

    # load each band for all state images, crop, and sort into the appropriate band list
for (row in 1:length(search_df_state$band)){#seq(length(search_df_state$band))
    #is it a swir 2 image?
  if (search_df_state$band[row] %in% c('B07','B12')){
    n = n+1
        #read in band image
    band_r <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
        #get image date and time
    doy_time = strsplit(sources(band_r), "[.]")[[1]][14]
    doy = substr(doy_time, 1, 7)
    date <- as.Date(as.integer(substr(doy,5,7)), origin = paste0(substr(doy,1,4), "-01-01"))
        #crop to ROI
            # If the state region is not CT, use that state's extent
    if(state!="CT"){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(roi)), roi)
            # If the state is CT and the band is in UTM19, align it to UTM 18 using resample().
    }else if(state=="CT"&str_detect(crs(band_r),"zone 18|Zone 18")){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(marsh_sf_list[["CT"]]),extend=T), marsh_sf_list[["CT"]])
    }else if(state=="CT"&str_detect(crs(band_r),"zone 19|Zone 19")){
      band_r_crop<-terra::mask(terra::resample(terra::project(band_r,terra::crs(ct18_temp)),ct18_temp), marsh_sf_list[["CT"]])
    }
        # set name as the image date
    names(band_r_crop)<-as.character(date)
        # add to band stack
    swir2_stack[[n]] <- band_r_crop
        # reset objects
    rm (band_r, band_r_crop)
    
    #is it a swir 1 image?
  }else if (search_df_state$band[row]=='B06' || (search_df_state$band[row]=='B11'&& substr(search_df_state$Collection[row],4,4)=="S")){
    o = o+1
        #read in band image
    band_r <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
        #get image date and time
    doy_time = strsplit(sources(band_r), "[.]")[[1]][14]
    doy = substr(doy_time, 1, 7)
    date <- as.Date(as.integer(substr(doy,5,7)), origin = paste0(substr(doy,1,4), "-01-01"))
        #crop to ROI
            # If the state region is not CT, use that state's extent
    if(state!="CT"){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(roi)), roi)
            # If the state is CT and the band is in UTM19, align it to UTM 18 using resample().
    }else if(state=="CT"&str_detect(crs(band_r),"zone 18|Zone 18")){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(marsh_sf_list[["CT"]]),extend=T), marsh_sf_list[["CT"]])
    }else if(state=="CT"&str_detect(crs(band_r),"zone 19|Zone 19")){
      band_r_crop<-terra::mask(terra::resample(terra::project(band_r,terra::crs(ct18_temp)),ct18_temp), marsh_sf_list[["CT"]])
    }
        # set name as the image date
    names(band_r_crop)<-as.character(date)
        # add to band stack
    swir1_stack[[o]] <- band_r_crop
    rm (band_r, band_r_crop)
    
    #is it a NIR image?
  }else if (search_df_state$band[row] %in% c('B05','B8A')){
    p = p+1
        #read in band image
    band_r <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
        #get image date and time
    doy_time = strsplit(sources(band_r), "[.]")[[1]][14]
    doy = substr(doy_time, 1, 7)
    date <- as.Date(as.integer(substr(doy,5,7)), origin = paste0(substr(doy,1,4), "-01-01"))
        #crop to ROI
            # If the state region is not CT, use that state's extent
    if(state!="CT"){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(roi)), roi)
            # If the state is CT and the band is in UTM19, align it to UTM 18 using resample().
    }else if(state=="CT"&str_detect(crs(band_r),"zone 18|Zone 18")){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(marsh_sf_list[["CT"]]),extend=T), marsh_sf_list[["CT"]])
    }else if(state=="CT"&str_detect(crs(band_r),"zone 19|Zone 19")){
      band_r_crop<-terra::mask(terra::resample(terra::project(band_r,terra::crs(ct18_temp)),ct18_temp), marsh_sf_list[["CT"]])
    }
        # set name as the image date
    names(band_r_crop)<-as.character(date)
        # add to band stack
    nir_stack[[p]] <- band_r_crop
    rm (band_r, band_r_crop)
    
    # is it a red image?
  }else if (search_df_state$band[row]=='B04'){
    q = q+1
        #read in band image
    band_r <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
        #get image date and time
    doy_time = strsplit(sources(band_r), "[.]")[[1]][14]
    doy = substr(doy_time, 1, 7)
    date <- as.Date(as.integer(substr(doy,5,7)), origin = paste0(substr(doy,1,4), "-01-01"))
        #crop to ROI
            # If the state region is not CT, use that state's extent
    if(state!="CT"){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(roi)), roi)
            # If the state is CT and the band is in UTM19, align it to UTM 18 using resample().
    }else if(state=="CT"&str_detect(crs(band_r),"zone 18|Zone 18")){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(marsh_sf_list[["CT"]]),extend=T), marsh_sf_list[["CT"]])
    }else if(state=="CT"&str_detect(crs(band_r),"zone 19|Zone 19")){
      band_r_crop<-terra::mask(terra::resample(terra::project(band_r,terra::crs(ct18_temp)),ct18_temp), marsh_sf_list[["CT"]])
    }
        # set name as the image date
    names(band_r_crop)<-as.character(date)
        # add to band stack
    red_stack[[q]] <- band_r_crop
    rm (band_r, band_r_crop)
    
    #is it a blue image?
  }else if (search_df_state$band[row]=='B02'){
    r = r+1
        #read in band image
    band_r <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
        #get image date and time
    doy_time = strsplit(sources(band_r), "[.]")[[1]][14]
    doy = substr(doy_time, 1, 7)
    date <- as.Date(as.integer(substr(doy,5,7)), origin = paste0(substr(doy,1,4), "-01-01"))
        #crop to ROI
            # If the state region is not CT, use that state's extent
    if(state!="CT"){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(roi)), roi)
            # If the state is CT and the band is in UTM19, align it to UTM 18 using resample().
    }else if(state=="CT"&str_detect(crs(band_r),"zone 18|Zone 18")){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(marsh_sf_list[["CT"]]),extend=T), marsh_sf_list[["CT"]])
    }else if(state=="CT"&str_detect(crs(band_r),"zone 19|Zone 19")){
      band_r_crop<-terra::mask(terra::resample(terra::project(band_r,terra::crs(ct18_temp)),ct18_temp), marsh_sf_list[["CT"]])
    }
        # set name as the image date
    names(band_r_crop)<-as.character(date)
        # add to band stack
    blue_stack[[r]] <- band_r_crop
    rm (band_r, band_r_crop)
    
    
    #is it a green image?
  }else if (search_df_state$band[row]=='B03'){
    s = s+1
        #read in band image
    band_r <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
        #get image date and time
    doy_time = strsplit(sources(band_r), "[.]")[[1]][14]
    doy = substr(doy_time, 1, 7)
    date <- as.Date(as.integer(substr(doy,5,7)), origin = paste0(substr(doy,1,4), "-01-01"))
        #crop to ROI
            # If the state region is not CT, use that state's extent
    if(state!="CT"){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(roi)), roi)
            # If the state is CT and the band is in UTM19, align it to UTM 18 using resample().
    }else if(state=="CT"&str_detect(crs(band_r),"zone 18|Zone 18")){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(marsh_sf_list[["CT"]]),extend=T), marsh_sf_list[["CT"]])
    }else if(state=="CT"&str_detect(crs(band_r),"zone 19|Zone 19")){
      band_r_crop<-terra::mask(terra::resample(terra::project(band_r,terra::crs(ct18_temp)),ct18_temp), marsh_sf_list[["CT"]])
    }
        # set name as the image date
    names(band_r_crop)<-as.character(date)
        # add to band stack
    green_stack[[s]] <- band_r_crop
    rm (band_r, band_r_crop)
    
 
    #is it a Quality image?
  }else if (search_df_state$band[row]=='Fmask'){
        # Set new band list index
    u = u+1
        #read in band image
    band_r <- terra::rast(paste0('/vsicurl/', search_df_state$Asset_Link[row]))
        #get image date and time
    doy_time = strsplit(sources(band_r), "[.]")[[1]][14]
    doy = substr(doy_time, 1, 7)
    date <- as.Date(as.integer(substr(doy,5,7)), origin = paste0(substr(doy,1,4), "-01-01"))
    time <- paste(substr(doy_time, 9, 10),substr(doy_time, 11, 12),sep=":")
        #crop to ROI
            # If the state region is not CT, use that state's extent
    if(state!="CT"){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(roi)), roi)
            # If the state is CT and the band is in UTM19, align it to UTM 18 using resample().
    }else if(state=="CT"&str_detect(crs(band_r),"zone 18|Zone 18")){
      band_r_crop <- terra::mask(terra::crop(band_r, terra::ext(marsh_sf_list[["CT"]]),extend=T), marsh_sf_list[["CT"]])
    }else if(state=="CT"&str_detect(crs(band_r),"zone 19|Zone 19")){
      band_r_crop<-terra::mask(terra::resample(terra::project(band_r,terra::crs(ct18_temp)),ct18_temp), marsh_sf_list[["CT"]])
    }
        # set name as the image date
    names(band_r_crop)<-as.character(date)
        # add to band stack
    fmask_stack[[u]] <- band_r_crop
    
    # also record the image information and add to a matching index list
    if (strsplit(sources(band_r), "[.]")[[1]][12] == 'S30'){
      date_list[[u]] <- paste0('S',as.character(date),'T',time)
    }else{
      date_list[[u]] <- paste0('L',as.character(date),'T',time)
    }
    rm (band_r, band_r_crop)
    
  }
  

# Save memory by processing ~50 images (all bands for each image) at a time
  #Also make sure it stops at a complete image (all images end at fmask)
  if(search_df_state$band[row]=='Fmask' & u==50){
    
#create a raster summary of nest characteristics that aligns with the SR band stacks
flooded_prop_mean<-rasterize(nests_state,fmask_stack[[1]],field="flooded_prop",fun="mean")%>%
  rename("flooded_prop_mean"="mean")
flooded_prop_max<-rasterize(nests_state,fmask_stack[[1]],field="flooded_prop",fun="max")%>%
  rename("flooded_prop_max"="max")
n_nests<-rasterize(nests_state,fmask_stack[[1]],fun="length")%>%
  rename("n_nests"="V1_length")
n_nests_suc<-rasterize(nests_state,fmask_stack[[1]],field="fate",fun="sum")%>%
  rename("n_nests_suc"="sum")
n_nests_flood<-rasterize(nests_state,fmask_stack[[1]],field="flooded_fate",fun="sum")%>%
  rename("n_nests_flood"="sum")

#turn into a stack
nest_stack<-rast(list(flooded_prop_max,flooded_prop_mean,n_nests,n_nests_flood,n_nests_suc))
 
#get cell numbers of pixels with nests
idx<-cells(n_nests) #returns cell numbers that are not NA

#extract stack contents at cells with nests
cells_nests<-terra::extract(nest_stack,idx)

cells_blue<-terra::extract(rast(blue_stack),idx)
names(cells_blue)<-lapply(names(cells_blue),function(x) paste("Blue",x,sep="_"))

cells_red<-terra::extract(rast(red_stack),idx)
names(cells_red)<-lapply(names(cells_red),function(x) paste("Red",x,sep="_"))

cells_nir<-terra::extract(rast(nir_stack),idx)
names(cells_nir)<-lapply(names(cells_nir),function(x) paste("NIR",x,sep="_"))

cells_swir1<-terra::extract(rast(swir1_stack),idx)
names(cells_swir1)<-lapply(names(cells_swir1),function(x) paste("SWIR1",x,sep="_"))

cells_swir2<-terra::extract(rast(swir2_stack),idx)
names(cells_swir2)<-lapply(names(cells_swir2),function(x) paste("SWIR2",x,sep="_"))

cells_green<-terra::extract(rast(green_stack),idx)
names(cells_green)<-lapply(names(cells_green),function(x) paste("Green",x,sep="_"))

cells_fmask<-terra::extract(rast(fmask_stack),idx)
names(cells_fmask)<-lapply(names(cells_fmask),function(x) paste("FMask",x,sep="_"))


nests_bands_cells<-do.call('cbind',list(cells_nests,cells_blue,cells_red,cells_nir,cells_swir1,cells_swir2,cells_green, cells_fmask))
names(nests_bands_cells)<-mapply(function(x,y) paste(x,y,sep = "_"),names(nests_bands_cells),seq(length(names(nests_bands_cells))))

nests_bands_cells<-nests_bands_cells%>%
  mutate(cell_ID=idx)%>%
  pivot_longer(cols = -c("flooded_prop_max_1","flooded_prop_mean_2","n_nests_3","n_nests_flood_4","n_nests_suc_5","cell_ID"),names_to = c("band","date"),names_sep = "_",values_to = "sr")%>%
  group_by(cell_ID,band,date)%>%
  summarise(across(everything(), first))# ***use the first value instead of the mean to retain accruate FMask values.

nests_bands_cells2<-nests_bands_cells%>%
  ungroup()%>%
  filter(!is.nan(sr))%>%
  pivot_wider(names_from = "band", values_from = "sr")

write.csv(nests_bands_cells2,paste0(outDir,"CT_nests_bands_cells_row",row,".csv"),row.names=F)
    
    # reset places to hold the cropped bands across all images
blue_stack<-green_stack<-red_stack<-nir_stack<-swir1_stack<-swir2_stack<-therm1_stack<-therm2_stack<-fmask_stack<- date_list<-list()

    # reset markers for each band list (should correspond with image number)
l <- m <- n <-o <- p<- q<- r<- s<- u<- 0

    # remove objects
rm(cells_nests,cells_blue,cells_green,cells_red,cells_nir,cells_swir1,cells_swir2,cells_fmask,
   nests_bands_cells,nests_bands_cells2,nest_stack,flooded_prop_mean,flooded_prop_max,n_nests,n_nests_flooded,
   n_nests_suc,idx)

    #clear unused memory
gc()
    
  }
}

close(pb)

#Once all image bands are read for the state, check if the images were all read correctly
stack_list<-list(fmask_stack,blue_stack,green_stack,red_stack,nir_stack,swir1_stack,swir2_stack,date_list)
names(stack_list)<-c("fmask_stack","blue_stack","green_stack","red_stack","nir_stack","swir1_stack","swir2_stack","date_list")
  # there should be the same number of images in each band stack as the total unique images in the state query
stack_read_errors<-unlist(lapply(stack_list, function(x) length(x)!=length(unique(search_df_state$Granule_ID))))
  # mark those that have more than the possible amount of images. These likely occur when the code breaks and needs to be re-run because it surpasses the image download allotment.
if(sum(stack_read_errors)>0){
  print("Warning: stack lists are uneven. Removing any null rows.")
#get which stacks have errors
stack_error_list<-stack_list[stack_read_errors]
if("swir2_stack"%in%names(stack_error_list)){
swir2_stack<-swir2_stack[-which(unlist(lapply(swir2_stack,function(x) length(x)==0)))]
}
if("swir1_stack"%in%names(stack_error_list)){
swir1_stack<-swir1_stack[-which(unlist(lapply(swir1_stack,function(x) length(x)==0)))]
}
if("nir_stack"%in%names(stack_error_list)){
nir_stack<-nir_stack[-which(unlist(lapply(nir_stack,function(x) length(x)==0)))]
}
if("red_stack"%in%names(stack_error_list)){
red_stack<-red_stack[-which(unlist(lapply(red_stack,function(x) length(x)==0)))]
}
if("green_stack"%in%names(stack_error_list)){
green_stack<-green_stack[-which(unlist(lapply(green_stack,function(x) length(x)==0)))]
}
if("blue_stack"%in%names(stack_error_list)){
blue_stack<-blue_stack[-which(unlist(lapply(blue_stack,function(x) length(x)==0)))]
}
if("fmask_stack"%in%names(stack_error_list)){
fmask_stack<-fmask_stack[-which(unlist(lapply(fmask_stack,function(x) length(x)==0)))]
}
if("date_list"%in%names(stack_error_list)){
date_list<-date_list[-which(unlist(lapply(date_list,function(x) length(x)==0)))]
}

}



```


#calculate nest characteristics in HLS raster cells. Then extract the nest characteristics and SR time series for each cell with nests.

```{r}
nests_state<-nests%>%
  filter(State=="CT",year>=2013,Species=="SALS")

#create a raster summary of nest characteristics that aligns with the SR band stacks
flooded_prop_mean<-rasterize(nests_state,fmask_stack[[1]],field="flooded_prop",fun="mean")%>%
  rename("flooded_prop_mean"="mean")
flooded_prop_max<-rasterize(nests_state,fmask_stack[[1]],field="flooded_prop",fun="max")%>%
  rename("flooded_prop_max"="max")
n_nests<-rasterize(nests_state,fmask_stack[[1]],fun="length")%>%
  rename("n_nests"="V1_length")
n_nests_suc<-rasterize(nests_state,fmask_stack[[1]],field="fate",fun="sum")%>%
  rename("n_nests_suc"="sum")
n_nests_flood<-rasterize(nests_state,fmask_stack[[1]],field="flooded_fate",fun="sum")%>%
  rename("n_nests_flood"="sum")

#turn into a stack
nest_stack<-rast(list(flooded_prop_max,flooded_prop_mean,n_nests,n_nests_flood,n_nests_suc))
 
#get cell numbers of pixels with nests
idx<-cells(n_nests) #returns cell numbers that are not NA

#extract stack contents at cells with nests
cells_nests<-terra::extract(nest_stack,idx)
t<-rast(blue_stack[1:5])
cells_blue<-terra::extract(rast(blue_stack),idx)
names(cells_blue)<-lapply(names(cells_blue),function(x) paste("Blue",x,sep="_"))

cells_red<-terra::extract(rast(red_stack),idx)
names(cells_red)<-lapply(names(cells_red),function(x) paste("Red",x,sep="_"))

cells_nir<-terra::extract(rast(nir_stack),idx)
names(cells_nir)<-lapply(names(cells_nir),function(x) paste("NIR",x,sep="_"))

cells_swir1<-terra::extract(rast(swir1_stack),idx)
names(cells_swir1)<-lapply(names(cells_swir1),function(x) paste("SWIR1",x,sep="_"))

cells_swir2<-terra::extract(rast(swir2_stack),idx)
names(cells_swir2)<-lapply(names(cells_swir2),function(x) paste("SWIR2",x,sep="_"))

cells_green<-terra::extract(rast(green_stack),idx)
names(cells_green)<-lapply(names(cells_green),function(x) paste("Green",x,sep="_"))

cells_fmask<-terra::extract(rast(fmask_stack),idx)
names(cells_fmask)<-lapply(names(cells_fmask),function(x) paste("FMask",x,sep="_"))


nests_bands_cells<-do.call('cbind',list(cells_nests,cells_blue,cells_red,cells_nir,cells_swir1,cells_swir2,cells_green, cells_fmask))
names(nests_bands_cells)<-mapply(function(x,y) paste(x,y,sep = "_"),names(nests_bands_cells),seq(length(names(nests_bands_cells))))

nests_bands_cells<-nests_bands_cells%>%
  mutate(cell_ID=idx)%>%
  pivot_longer(cols = -c("flooded_prop_max_1","flooded_prop_mean_2","n_nests_3","n_nests_flood_4","n_nests_suc_5","cell_ID"),names_to = c("band","date"),names_sep = "_",values_to = "sr")%>%
  group_by(cell_ID,band,date)%>%
  summarise(across(everything(), mean,na.rm=T))

nests_bands_cells2<-nests_bands_cells%>%
  ungroup()%>%
  filter(!is.nan(sr))%>%
  pivot_wider(names_from = "band", values_from = "sr")

write.csv(nests_bands_cells2,paste0(outDir,"CT_nests_bands_cells_row1676.csv"),row.names=F)
```


# Extract band values at pixels that contain nest locations
```{r}
#name the bands by date
names(blue_stack) <- unlist(date_list)
names(green_stack) <- unlist(date_list)
names(red_stack) <- unlist(date_list)
names(nir_stack) <- unlist(date_list)
names(swir1_stack) <- unlist(date_list)
names(swir2_stack) <- unlist(date_list)
names(fmask_stack) <- unlist(date_list)

# create a list to hold the pixel values for each nest
blue_pix<-green_pix<-red_pix<-nir_pix<-swir1_pix<-swir2_pix<-fmask_pix<-list()

#Do this one state at a time (too big otherwise)
nests_state<-nests%>%
  filter(State=="CT"&year>=2013&Species=="SALS")


  # extract blue
blue_pix[[i]]<-lapply(blue_stack,function(x) terra::extract(x,terra::project(vect(nests_state[i,]), crs(x))))
blue_pix[[i]]<-do.call('rbind',lapply(blue_pix[[i]],function(x){
  names(x)<-c("ID","blue")
  return(x)
}))
blue_pix[[i]]<-blue_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = blue)

for (i in 1:nrow(nests_state)){
# extract green
green_pix[[i]]<-lapply(green_stack,function(x) terra::extract(x,terra::project(vect(nests_state[i,]), crs(x))))
green_pix[[i]]<-do.call('rbind',lapply(green_pix[[i]],function(x){
  names(x)<-c("ID","green")
  return(x)
}))
green_pix[[i]]<-green_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = green)


# extract red
red_pix[[i]]<-lapply(red_stack,function(x) terra::extract(x,terra::project(vect(nests_state[i,]), crs(x))))
red_pix[[i]]<-do.call('rbind',lapply(red_pix[[i]],function(x){
  names(x)<-c("ID","red")
  return(x)
}))
red_pix[[i]]<-red_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = red)


# extract nir
nir_pix[[i]]<-lapply(nir_stack,function(x) terra::extract(x,terra::project(vect(nests_state[i,]), crs(x))))
nir_pix[[i]]<-do.call('rbind',lapply(nir_pix[[i]],function(x){
  names(x)<-c("ID","nir")
  return(x)
}))
nir_pix[[i]]<-nir_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = nir)


# extract swir1
swir1_pix[[i]]<-lapply(swir1_stack,function(x) terra::extract(x,terra::project(vect(nests_state[i,]), crs(x))))
swir1_pix[[i]]<-do.call('rbind',lapply(swir1_pix[[i]],function(x){
  names(x)<-c("ID","swir1")
  return(x)
}))
swir1_pix[[i]]<-swir1_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = swir1)


# extract swir2
swir2_pix[[i]]<-lapply(swir2_stack,function(x) terra::extract(x,terra::project(vect(nests_state[i,]), crs(x))))
swir2_pix[[i]]<-do.call('rbind',lapply(swir2_pix[[i]],function(x){
  names(x)<-c("ID","swir2")
  return(x)
}))
swir2_pix[[i]]<-swir2_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = swir2)


#extract Fmask
fmask_pix[[i]]<-lapply(fmask_stack,function(x) terra::extract(x,terra::project(vect(nests_state[i,]), crs(x))))
fmask_pix[[i]]<-do.call('rbind',lapply(fmask_pix[[i]],function(x){
  names(x)<-c("ID","fmask")
  return(x)
}))
fmask_pix[[i]]<-fmask_pix[[i]]%>%
    rownames_to_column(var="date_time")%>%
    pivot_wider(names_from=date_time,values_from = fmask)

}
  #combine all the band extraction columns for each nest into one table with rbind
blue_pix2<-do.call('rbind',blue_pix)%>%
  arrange(ID)%>%
  cbind(st_drop_geometry(nests_state[,1:3]))%>%
  dplyr::select(-ID)%>%
  pivot_longer(cols=-c(nest_id,site,year), names_to = c("Date","Time"),names_prefix = "^.{1}",names_sep = "T",
               values_to = "Blue")%>%
  drop_na(Blue)%>%
  mutate(Date=ymd(Date))%>%
  arrange(nest_id,Date)

green_pix2<-do.call('rbind',green_pix)%>%
  arrange(ID)%>%
  cbind(st_drop_geometry(nests_state[,1:3]))%>%
  dplyr::select(-ID)%>%
  pivot_longer(cols=-c(nest_id,site,year), names_to = c("Date","Time"),names_prefix = "^.{1}",names_sep = "T",
               values_to = "Green")%>%
  drop_na(Green)%>%
  mutate(Date=ymd(Date))%>%
  arrange(nest_id,Date)

red_pix2<-do.call('rbind',red_pix)%>%
  arrange(ID)%>%
  cbind(st_drop_geometry(nests_state[,1:3]))%>%
  dplyr::select(-ID)%>%
  pivot_longer(cols=-c(nest_id,site,year), names_to = c("Date","Time"),names_prefix = "^.{1}",names_sep = "T",
               values_to = "Red")%>%
  drop_na(Red)%>%
  mutate(Date=ymd(Date))%>%
  arrange(nest_id,Date)

nir_pix2<-do.call('rbind',nir_pix)%>%
  arrange(ID)%>%
  cbind(st_drop_geometry(nests_state[,1:3]))%>%
  dplyr::select(-ID)%>%
  pivot_longer(cols=-c(nest_id,site,year), names_to = c("Date","Time"),names_prefix = "^.{1}",names_sep = "T",
               values_to = "NIR")%>%
  drop_na(NIR)%>%
  mutate(Date=ymd(Date))%>%
  arrange(nest_id,Date)

swir1_pix2<-do.call('rbind',swir1_pix)%>%
  arrange(ID)%>%
  cbind(st_drop_geometry(nests_state[,1:3]))%>%
  dplyr::select(-ID)%>%
  pivot_longer(cols=-c(nest_id,site,year), names_to = c("Date","Time"),names_prefix = "^.{1}",names_sep = "T",
               values_to = "SWIR1")%>%
  drop_na(SWIR1)%>%
  mutate(Date=ymd(Date))%>%
  arrange(nest_id,Date)

swir2_pix2<-do.call('rbind',swir2_pix)%>%
  arrange(ID)%>%
  cbind(st_drop_geometry(nests_state[,1:3]))%>%
  dplyr::select(-ID)%>%
  pivot_longer(cols=-c(nest_id,site,year), names_to = c("Date","Time"),names_prefix = "^.{1}",names_sep = "T",
               values_to = "SWIR2")%>%
  drop_na(SWIR2)%>%
  mutate(Date=ymd(Date))%>%
  arrange(nest_id,Date)

fmask_pix2<-do.call('rbind',fmask_pix)%>%
  arrange(ID)%>%
  cbind(st_drop_geometry(nests_state[,1:3]))%>%
  dplyr::select(-ID)%>%
  pivot_longer(cols=-c(nest_id,site,year), names_to = c("Date","Time"),names_prefix = "^.{1}",names_sep = "T",
               values_to = "FMask")%>%
  drop_na(FMask)%>%
  mutate(Date=ymd(Date))%>%
  arrange(nest_id,Date)

#combine into one dataframe that has dates with all band observations for each nest
#all band dataframes should have the same number of observations
nrow(fmask_pix2)==nrow(swir2_pix2)
nrow(fmask_pix2)==nrow(swir1_pix2)
nrow(fmask_pix2)==nrow(nir_pix2)
nrow(fmask_pix2)==nrow(red_pix2)
nrow(fmask_pix2)==nrow(green_pix2)
nrow(fmask_pix2)==nrow(blue_pix2)

nests_all_bands<-do.call('cbind', list(blue_pix2,green_pix2[,ncol(green_pix2)],red_pix2[,ncol(red_pix2)],nir_pix2[,ncol(nir_pix2)],
                                       swir1_pix2[,ncol(swir1_pix2)],swir2_pix2[,ncol(swir2_pix2)],fmask_pix2[,ncol(fmask_pix2)]))
nests_all_bands<-write.csv(nests_all_bands,paste0(outDir,"CT_nests_all_HLS_bands.csv"),row.names=F)
```

